---
title: "Untitled"
author: "Keyi Wang"
date: "10/7/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
library(patchwork)
library(p8105.datasets)

```


```{r, include=FALSE}
 data("instacart")
```
How many aisles are there, and which aisles are the most items ordered from?
```{r}
## there are 134 different aisles id
instacart %>%
select(aisle_id) %>%
  distinct() %>%
  summarize((n_obs = n())) 

## the most popular aisle is aisle 83 which has been ordered 150609 times
instacart %>%
select(aisle_id) %>%
  count(aisle_id) %>%
mutate(
  number_of_aisle = n
) %>%
  arrange(desc(number_of_aisle)) 
```

Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.
```{r}
instacart %>%
select(aisle_id) %>%
  count(aisle_id) %>%
mutate(
   aisle_id = factor(aisle_id),
   number_of_aisle = n
) %>%
  filter(number_of_aisle > 10000) %>%
 ggplot(aes(x = aisle_id, y = number_of_aisle,color = aisle_id )) +
  geom_point() +
  labs(
    title = "Plot of Aisles Ordered More Than 10000 Items",
    x = "Aisle ID",
    y = "Number of Items Ordered"
  ) +
   viridis::scale_color_viridis(
    name = "Aisle ID", 
    discrete = TRUE
  ) +
   theme(legend.position = "bottom")

```
Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.
```{r}
##generating dataset for packaged vegetables fruits with top3 items
pvf =
instacart %>%
  filter(aisle == "packaged vegetables fruits" )  %>%
  select(aisle, product_name) %>%
  count(aisle, product_name) %>%
  arrange(desc(n))  %>%
  filter(n > 4059) 

##generating dataset for dog food care with top 3 items
dfc = 
instacart %>%
 filter(aisle == "dog food care")%>%
 select(aisle, product_name) %>%
  count(aisle, product_name) %>%
  arrange(desc(n)) %>%
 filter(n > 25) 

##generating dataset for baking ingredients with top 3 items
bi =
instacart %>%
 filter(aisle == "baking ingredients")%>%
  select(aisle, product_name) %>%
  count(aisle, product_name) %>%
  arrange(desc(n)) %>%
 filter(n > 329)

## combining above dataset to make the desired table
table1 =
bind_rows(pvf,dfc,bi) %>%
knitr::kable()
table1 
```
Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).
```{r}
## manipulation for cream dataset
cream =
instacart %>%
  select(order_dow,order_hour_of_day,product_name,) %>%
 filter(product_name == "Coffee Ice Cream") %>%
  arrange(order_dow)%>%
  mutate(
    mean_0 = mean(order_hour_of_day[order_dow ==0]),
     mean_1 = mean(order_hour_of_day[order_dow ==1]),
     mean_2 = mean(order_hour_of_day[order_dow ==2]),
     mean_3 = mean(order_hour_of_day[order_dow ==3]),
     mean_4 = mean(order_hour_of_day[order_dow ==4]),
     mean_5 = mean(order_hour_of_day[order_dow ==5]),
     mean_6 = mean(order_hour_of_day[order_dow ==6])
  ) %>%
  select(-order_hour_of_day) %>%
  distinct() %>%
  mutate(
    mean_hour_of_the_day = c(13.8,14.3,15.4,15.3,15.2,12.3,13.8)
  ) %>%
 select(product_name,order_dow,mean_hour_of_the_day) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from= mean_hour_of_the_day
  )%>%
rename( Sun ="0" ,
        Mon = "1",
        Tue = "2",
        Wed = "3",
        Thur = "4",
        Fri = "5" ,
        Sat = "6"
        )
## manipulation for apple dataset
apple=
instacart %>%
  select(order_dow,order_hour_of_day,product_name,) %>%
 filter(product_name == "Pink Lady Apples") %>%
  arrange(order_dow)%>%
  mutate(
    mean_0 = mean(order_hour_of_day[order_dow ==0]),
     mean_1 = mean(order_hour_of_day[order_dow ==1]),
     mean_2 = mean(order_hour_of_day[order_dow ==2]),
     mean_3 = mean(order_hour_of_day[order_dow ==3]),
     mean_4 = mean(order_hour_of_day[order_dow ==4]),
     mean_5 = mean(order_hour_of_day[order_dow ==5]),
     mean_6 = mean(order_hour_of_day[order_dow ==6])
  ) %>%
  select(-order_hour_of_day) %>%
  distinct() %>%
  mutate(
    mean_hour_of_the_day = c(13.4,11.4,11.7,14.3,11.6,12.8,12.0)
  ) %>%
 select(product_name,order_dow,mean_hour_of_the_day) %>% 
    pivot_wider(
    names_from = order_dow,
    values_from = mean_hour_of_the_day
  )%>% 
rename( Sun ="0" ,
        Mon = "1",
        Tue = "2",
        Wed = "3",
        Thur = "4",
        Fri = "5" ,
        Sat = "6"
        )
## combining above dataset
table2 =
bind_rows(apple,cream) %>%
knitr::kable()
table2
 

```


