---
title: "Untitled"
author: "Keyi Wang"
date: "10/7/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
library(patchwork)
library(p8105.datasets)
library(httr)
library(jsonlite)
```


```{r, include=FALSE}
 data("instacart")
 data("brfss_smart2010")

```
How many aisles are there, and which aisles are the most items ordered from?
```{r}
## there are 134 different aisles id
instacart %>%
select(aisle_id) %>%
  distinct() %>%
  summarize((n_obs = n())) 

## the most popular aisle is aisle 83 which has been ordered 150609 times
cart_1 = instacart %>%
select(aisle_id) %>%
  count(aisle_id) %>%
mutate(
  number_of_item = n
) %>%
  arrange(desc(number_of_item)) 
```

Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.

```{r}
cart_1 %>%
  filter(number_of_item >10000)%>%
  mutate(
   aisle_id = factor(aisle_id),
  aisle_id = forcats::fct_reorder(aisle_id, number_of_item )) %>%
  ggplot(aes(x = aisle_id, y = number_of_item,color = aisle_id))+
  geom_col() +
  labs(
    title = "Plot of Aisles Ordered More Than 10000 Items",
    x = "Aisle ID",
    y = "Number of Items Ordered"
  ) +
   viridis::scale_color_viridis(
    name = "Aisle ID", 
    discrete = TRUE
  ) +
   theme(legend.position = "bottom")

```

Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.
```{r}
##generating dataset for packaged vegetables fruits with top3 items
pvf =
instacart %>%
  filter(aisle == "packaged vegetables fruits" )  %>%
  select(aisle, product_name) %>%
  count(aisle, product_name) %>%
  arrange(desc(n))  %>%
  filter(n > 4059) 

##generating dataset for dog food care with top 3 items
dfc = 
instacart %>%
 filter(aisle == "dog food care")%>%
 select(aisle, product_name) %>%
  count(aisle, product_name) %>%
  arrange(desc(n)) %>%
 filter(n > 25) 

##generating dataset for baking ingredients with top 3 items
bi =
instacart %>%
 filter(aisle == "baking ingredients")%>%
  select(aisle, product_name) %>%
  count(aisle, product_name) %>%
  arrange(desc(n)) %>%
 filter(n > 329)

## combining above dataset to make the desired table
table1 =
bind_rows(pvf,dfc,bi) %>%
knitr::kable()
table1 
```

Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).

```{r}
instacart %>%
  select(order_dow,order_hour_of_day,product_name,) %>%
 filter(product_name == "Pink Lady Apples"|product_name == "Coffee Ice Cream") %>%
  arrange(order_dow) %>%
  group_by(product_name, order_dow) %>% 
  summarize(mean_hour = mean(order_hour_of_day)) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from = mean_hour
  ) %>%
  rename( Sun = "0" ,
        Mon = "1",
        Tue = "2",
        Wed = "3",
        Thur = "4",
        Fri = "5" ,
        Sat = "6"
        )

```


format the data to use appropriate variable names;
focus on the “Overall Health” topic
include only responses from “Excellent” to “Poor”
organize responses as a factor taking levels ordered from “Poor” to “Excellent”
```{r}
## clean and change variable
brfss = 
  brfss_smart2010 %>%
  janitor::clean_names() %>%
  rename( state = "locationabbr",
        location = "locationdesc"
        )
### arrange response data based on topic(Overall Health) from poor to excellent
 brfss %>%
  filter(topic == "Overall Health"|response == "Excellent"|response == "Very good"
         |response == "Good"|response == "Fair"|response == "Poor")  %>%
  select(topic,response) %>%
  mutate(
    response = factor(response, levels = c("Poor","Fair","Good","Very good","Excellent"))
  ) %>%
arrange(response)

```
In 2002, which states were observed at 7 or more locations? What about in 2010?
```{r}
## data manipulation to know which states were observed 7 or more locations in 2002
brfss %>%
filter(year == "2002") %>%
  select(year,state,location) %>%
  group_by(state,location) %>%
  distinct(location) %>%
  arrange(state) %>%
  group_by(state) %>% 
  summarize(n_obs = n()) %>%
  filter(n_obs >= 7)

## data manipulation to know which states were observed 7 or more locations in 2010
brfss %>%
filter(year == "2010") %>%
  select(year,state,location) %>%
  group_by(state,location) %>%
  distinct(location) %>%
  arrange(state) %>%
  group_by(state) %>% 
  summarize(n_obs = n()) %>%
  filter(n_obs >= 7)
```

Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state (that is, make a plot showing a line for each state across years – the geom_line geometry and group aesthetic will help).

```{r}
brfss %>%
  filter(response == "Excellent")  %>%
  select(year,state,location,data_value) %>%
  drop_na() %>%
  group_by(year,state) %>%
  summarize(ave_within_state_overtime = mean(data_value)) %>%
  ggplot(aes(x = year,y = ave_within_state_overtime,color = state)) +
  geom_line() +
  labs(
    title = " Plot of Average Data Value Over Time Within a State ",
    x = "Year",
    y = " BRFSS Data Value Within State From 2002 to 2010",
    caption = "Data from BRFSS "
  )
```

Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.

```{r}
  brfss %>%
  filter(topic == "Overall Health"|response == "Excellent"|response == "Very good"
         |response == "Good"|response == "Fair"|response == "Poor")  %>%
   mutate(
    response = factor(response, levels = c("Poor","Fair","Good","Very good","Excellent"))
  ) %>%
arrange(response)%>%
  filter(year == "2006" | year == "2010") %>% 
  filter(state == "NY") %>% 
  group_by(response) %>%  
  ggplot(aes(x = data_value, fill = response)) +
  # set transparency
  geom_density(alpha = 0.5) +
  # create a two panel plot for responses among locations in NY State
  facet_grid(year ~ response) +
  # add title, labels for x- and y- labels and caption
  labs(
    title = "Two Panel Plot for Responses among Locations in NY State",
    x = "Data Value",
    y = "Density"
  )




```


Load, tidy, and otherwise wrangle the data. Your final dataset should include all originally observed variables and values; have useful variable names; include a weekday vs weekend variable; and encode data with reasonable variable classes. Describe the resulting dataset (e.g. what variables exist, how many observations, etc).
```{r}
accel_data = read_csv(file = "./data/accel_data.csv")
tidy_accel_data = 
accel_data %>%
janitor::clean_names() %>%
pivot_longer(
  activity_1:activity_1440, ## choose the column you want to combine
  names_to = "nth_minute",  ###name the new-made column
  names_prefix = "activity_",
  values_to = "activity" 
  ) %>% 
  mutate(
    week = as.factor(week),
    nth_minute = as.numeric(nth_minute),
    day_id = as.integer(day_id),
    day = forcats::fct_relevel(day,c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday"))) %>% 
    arrange(day) %>% 
    mutate(weekday_weekend = case_when(
    day %in% c("Monday","Tuesday","Wednesday","Thursday","Friday")~ "weekday",
    day %in% c("Saturday","Sunday")~ "weekend",
    TRUE     ~ ""
  )) 

```
Traditional analyses of accelerometer data focus on the total activity over the day. Using your tidied dataset, aggregate accross minutes to create a total activity variable for each day, and create a table showing these totals. Are any trends apparent?

```{r}
tidy_accel_data %>%
  group_by(week, day,weekday_weekend) %>%
  summarize(
    total_activity = sum(activity)
  ) %>% 
 knitr::kable()

### since it is not very easy for us to find an exact trend in a 
### table, I decided to it into a plot.
  table_data =
  tidy_accel_data %>%
  group_by(week, day) %>%
  summarize(
    sum_of_day = sum(activity)
  )  %>%
    ungroup(week,day)%>%
    mutate(
      day_number  =  row_number()
    )
  
table_data %>%
  ggplot(aes(x = day_number, y = sum_of_day)) +
  geom_point(aes(color = day_number), alpha = 0.5) +
  geom_line(aes(color = day_number)) +
  # add title, labels for x- and y- axis and caption
  labs(
    title = "Trend Plot for Activity Across 35 days ",
    x = "Days",
    y = "Total Activity Counts for Each Day",
    caption = "Data from the Advanced Cardiac Care Center of Columbia University Medical Center"
  ) +
  scale_y_continuous(
    # make the y-axis labels a bit prettier
    breaks = c(0, 200000, 400000, 600000, 800000),
    labels = c("0", "200000", "400000", "600000", "800000")
    )

```


Accelerometer data allows the inspection activity over the course of the day. Make a single-panel plot that shows the 24-hour activity time courses for each day and use color to indicate day of the week. Describe in words any patterns or conclusions you can make based on this graph.

```{r}
tidy_accel_data %>% 
  group_by(day) %>% 
  mutate(
  hour_per_day = ceiling(nth_minute/60)) %>% 
  group_by(day, hour_per_day) %>% 
  summarize(sum_by_hour = sum(activity)) %>% 
  ggplot(aes(x = hour_per_day, y = sum_by_hour)) +
  geom_point(aes(color = day)) +
  geom_line(aes(color = day)) +
  labs(
    title = "Plot for 24-hour Activity Time Courses for Each Day",
    x = "Hour in a Day",
    y = "Total Activity for Each Hour"
    ) +
    scale_y_continuous(
    breaks = c(0, 100000, 200000, 300000),
    labels = c("0", "100000", "200000", "300000")
  ) +
    scale_x_continuous(
    breaks = c(0, 4, 8, 12, 16, 20, 24),
    labels = c("0", "4", "8", "12", "16", "20", "24"))
  

 

```


