---
title: "Untitled"
author: "Keyi Wang"
date: "10/7/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
library(patchwork)
library(p8105.datasets)
library(httr)
library(jsonlite)
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6, 
  out.width = "90%"
)


options(
  ggplot2.countinuous.colour = "viridis",
  ggplot2.countinuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


```{r, include=FALSE}
 data("instacart")
 data("brfss_smart2010")

```
How many aisles are there, and which aisles are the most items ordered from?
```{r}
## there are 134 different aisles id
instacart %>%
select(aisle_id) %>%
  distinct() %>%
  summarize((n_obs = n())) 

## the most popular aisle is aisle 83 which has been ordered 150609 times
instacart %>%
  group_by(aisle) %>%
  count(aisle_id) %>%
mutate(
  number_of_item = n
) %>%
  select(-n)%>%
  arrange(desc(number_of_item)) 
```

Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.

```{r}
##plot showing the number of items ordered in ecah aisle from 
## the least popular to most popular aisles
cart_1 = instacart %>%
select(aisle_id) %>%
  count(aisle_id) %>%
mutate(
  number_of_item = n
) %>%
  arrange(desc(number_of_item)) 

cart_1 %>%
  filter(number_of_item > 10000) %>%
  mutate(
   aisle_id = factor(aisle_id),
  aisle_id = forcats::fct_reorder(aisle_id, number_of_item )) %>%
  ggplot(aes(x = aisle_id, y = number_of_item,color = aisle_id))+
  geom_col() +
  labs(
    title = "Plot of Aisles Ordered More Than 10000 Items",
    x = "Aisle ID",
    y = "Number of Items Ordered"
  ) +
   viridis::scale_color_viridis(
    name = "Aisle ID", 
    discrete = TRUE
  ) +
   theme(legend.position = "bottom")

```

Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.
```{r}
item_table = instacart %>% 
  group_by(aisle, product_name) %>% 
  filter(aisle == "baking ingredients" | aisle == "dog food care" |  aisle == "packaged vegetables fruits") %>% 
  summarize(number_sale = n()) %>% 
  filter(min_rank(desc(number_sale)) < 4) %>% 
  arrange(desc(number_sale)) %>% 
  knitr::kable()
item_table
```

Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).

```{r}
instacart %>%
  select(order_dow,order_hour_of_day,product_name,) %>%
 filter(product_name == "Pink Lady Apples"|product_name == "Coffee Ice Cream") %>%
  arrange(order_dow) %>%
  group_by(product_name, order_dow) %>% 
  summarize(mean_hour = mean(order_hour_of_day)) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from = mean_hour
  ) %>%
  rename( Sun = "0" ,
        Mon = "1",
        Tue = "2",
        Wed = "3",
        Thur = "4",
        Fri = "5" ,
        Sat = "6"
        )%>%
knitr::kable(digit = 1)
```


Short description of the dataset:
This dataset contains information about online grocery orders from more than 200,000 Instacart users and there are `r count(instacart)` observations of 131209 customers in the year of 2017, where each row in the dataset is a product from an order. 
There are total 15 variables:
* order_id: order identifier
* product_id: product identifier
* add_to_cart_order: order in which each product was added to cart
* reordered: 1 if this prodcut has been ordered by this user in the past, 0 otherwise
* user_id: customer identifier
* eval_set: which evaluation set this order belongs in (Note that the data for use in this class is exclusively from the “train” eval_set)
* order_number: the order sequence number for this user (1=first, n=nth)
* order_dow: the day of the week on which the order was placed
* order_hour_of_day: the hour of the day on which the order was placed
* days_since_prior_order: days since the last order, capped at 30, NA if order_number=1
* product_name: name of the product
* aisle_id: aisle identifier
* department_id: department identifier
* aisle: the name of the aisle
* department: the name of the department

While doing data manipulation, I found the item_table I made most useful as We can find the most popular product within each aisle. Perhaps, we can use this data to prepare the inventory and keep on track of how many inventory the store should have on hand to sale. And if we combine this with time of order or date of order, we can maybe find a pattern for certain products and their best selling dates, (for example, turkey and thanksgiving day) to properly prepare our inventory in case that some certain goods would be out-of-stock on certain period of time and having excessive inventory for other times. 



##problem2

format the data to use appropriate variable names;
focus on the “Overall Health” topic
include only responses from “Excellent” to “Poor”
organize responses as a factor taking levels ordered from “Poor” to “Excellent”
```{r}
## clean and change variable
brfss = 
  brfss_smart2010 %>%
  janitor::clean_names() %>%
  rename( state = "locationabbr",
        location = "locationdesc"
        )
### arrange response data based on topic(Overall Health) from poor to excellent
 brfss %>%
  filter(topic == "Overall Health"|response == "Excellent"|response == "Very good"
         |response == "Good"|response == "Fair"|response == "Poor")  %>%
  select(topic,response) %>%
  mutate(
    response = factor(response, levels = c("Poor","Fair","Good","Very good","Excellent"))
  ) %>%
arrange(response)

```
In 2002, which states were observed at 7 or more locations? What about in 2010?
```{r}
## data manipulation to know which states were observed 7 or more locations in 2002
brfss %>%
filter(year == "2002") %>%
  select(year,state,location) %>%
  group_by(state,location) %>%
  distinct(location) %>%
  arrange(state) %>%
  group_by(state) %>% 
  summarize(n_obs = n()) %>%
  filter(n_obs >= 7)

## data manipulation to know which states were observed 7 or more locations in 2010
brfss %>%
filter(year == "2010") %>%
  select(year,state,location) %>%
  group_by(state,location) %>%
  distinct(location) %>%
  arrange(state) %>%
  group_by(state) %>% 
  summarize(n_obs = n()) %>%
  filter(n_obs >= 7)
```
Aswer to above questions:
In 2002, the states that were observed at 7 or more locations are Connecticut, Florida, Massachusetts, North Carolina, New Jersey, Pennsylvania.
In 2010, the states that were observed at 7 or more locations are California, Colorado, Florida, Massachusetts, Maryland, North Carolina, Nebraska, New Jersey, New York, Ohio, Pannsylvania, South Carolina, Texas, Washington.


Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state (that is, make a plot showing a line for each state across years – the geom_line geometry and group aesthetic will help).

```{r}
brfss %>%
  filter(response == "Excellent")  %>%
  select(year,state,location,data_value) %>%
  drop_na() %>%
  group_by(year,state) %>%
  summarize(ave_within_state_overtime = mean(data_value)) %>%
  ggplot(aes(x = year,y = ave_within_state_overtime,color = state)) +
  geom_line() +
  labs(
    title = " Plot of Average Data Value Over Time Within a State ",
    x = "Year",
    y = " BRFSS Data Value From 2002 to 2010",
    caption = "Data from BRFSS "
  )
```

The average data value for each state across its locations(counties) from 2002 to 2010 is relatively stable (which means there is no big change/jump through this period of time).


Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.

```{r}
  brfss %>%
  filter(topic == "Overall Health"|response == "Excellent"|response == "Very good"
         |response == "Good"|response == "Fair"|response == "Poor")  %>%
   mutate(
    response = factor(response, levels = c("Poor","Fair","Good","Very good","Excellent"))
  ) %>%
arrange(response)%>%
  filter(year == "2006" | year == "2010") %>% 
  filter(state == "NY") %>% 
  group_by(response) %>%  
  ggplot(aes(x = data_value, fill = response)) +
  geom_density(alpha = 0.5) +
  facet_grid(year ~ response) +
  labs(
    title = "Two Panel Plot for Responses among Locations in NY State",
    x = "Data Value",
    y = "Density"
  )

```
Within the state of NY, the distributions of each response given the same response is mostly similar between the year of 2006 and 2010. The Fair response differed a little, but it is not terribly different. 




Load, tidy, and otherwise wrangle the data. Your final dataset should include all originally observed variables and values; have useful variable names; include a weekday vs weekend variable; and encode data with reasonable variable classes. Describe the resulting dataset (e.g. what variables exist, how many observations, etc).
```{r}
accel_data = read_csv(file = "./data/accel_data.csv")
tidy_accel_data = 
accel_data %>%
janitor::clean_names() %>%
pivot_longer(
  activity_1:activity_1440,
  names_to = "nth_minute", 
  names_prefix = "activity_",
  values_to = "activity" 
  ) %>% 
  mutate(
    week = as.factor(week),
    nth_minute = as.numeric(nth_minute),
    day_id = as.integer(day_id),
    day = forcats::fct_relevel(day,c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday"))) %>% 
    arrange(day) %>% 
    mutate(weekday_weekend = case_when(
    day %in% c("Monday","Tuesday","Wednesday","Thursday","Friday")~ "weekday",
    day %in% c("Saturday","Sunday")~ "weekend",
    TRUE     ~ ""
  )) 

```
Traditional analyses of accelerometer data focus on the total activity over the day. Using your tidied dataset, aggregate accross minutes to create a total activity variable for each day, and create a table showing these totals. Are any trends apparent?

```{r}
tidy_accel_data %>%
  group_by(week, day,weekday_weekend) %>%
  summarize(
    total_activity = sum(activity)
  ) %>% 
 knitr::kable()

### since it is not very easy for us to find an exact trend in a 
### table, I decided to it into a plot.
  table_data =
  tidy_accel_data %>%
  group_by(week, day) %>%
  summarize(
    sum_of_day = sum(activity)
  )  %>%
    ungroup(week,day)%>%
    mutate(
      day_number  =  row_number()
    )
  
table_data %>%
  ggplot(aes(x = day_number, y = sum_of_day)) +
  geom_point(aes(color = day_number), alpha = 0.5) +
  geom_line(aes(color = day_number)) +
  labs(
    title = "Trend Plot for Activity Across 35 days ",
    x = "Days",
    y = "Total Activity Counts for Each Day",
    caption = "Data from the Advanced Cardiac Care Center of Columbia University Medical Center"
  ) +
  scale_y_continuous(
    breaks = c(0, 200000, 400000, 600000, 800000),
    labels = c("0", "200000", "400000", "600000", "800000")
    )

```


This dataset is called accel_data which  uses five weeks of accelerometer data collected on a 63 year-old male with BMI 25, who was admitted to the Advanced Cardiac Care Center of Columbia University Medical Center and diagnosed with congestive heart failure (CHF).

The variables are:

* week: the number of the week of this man's data record
* day_id: the number of the day of this man's data record
* day: the day of week of this man's data record
* minute_in_a_day: the minute of a day of this man's data record
* activity_count: the activity counts for each minute of a 24-hour day starting at midnight for this man's data record
* weekday: to indicate whether it is a weekday or a weekend for this man's data record


Accelerometer data allows the inspection activity over the course of the day. Make a single-panel plot that shows the 24-hour activity time courses for each day and use color to indicate day of the week. Describe in words any patterns or conclusions you can make based on this graph.

```{r}
tidy_accel_data %>% 
  group_by(day) %>% 
  mutate(
  hour_per_day = ceiling(nth_minute/60)) %>% 
  ## sum up one-hour activity
  group_by(day_id,day, hour_per_day) %>% 
  summarize(sum_by_hour = sum(activity)) %>% 
  ggplot(aes(x = hour_per_day, y = sum_by_hour)) +
  geom_point(aes(color = day)) +
  geom_line(aes(color = day)) +
  labs(
    title = "Plot for 24-hour Activity Time Courses for Each Day",
    x = "Hour in a Day",
    y = "Total Activity for Each Hour"
    ) +
    scale_y_continuous(
    breaks = c(0, 100000, 200000, 300000),
    labels = c("0", "100000", "200000", "300000")
  )+
    scale_x_continuous(
    breaks = c(0, 4, 8, 12, 16, 20, 24),
    labels = c("0", "4", "8", "12", "16", "20", "24"))



```

By summing up the each one- hour actvity, I create a plot showing the trend of activity within 35 days based on 24-hour time course. 
According to the plot above, we can see that the man is inactive during 0AM - 8AM, and then maintained a stable level of activeness for the rest of day from 8AM to 8PM. However, he moved around a lot at Friday nights and Sunday mornings relatively. Then his activity counts gradually decreased after 8PM.

